Pteropod biomarker analysis

### 2018-03-02 index.Rmd
messing with plotly, added heatmap

library(tidyverse)
library(vegan)
library(ggord)
library(scales)
library(effects)
library(shiny)

@@

@@

  p <- ggplot(prd_vl, aes_string(y = names(prd_vl)[2], x = names(prd_vl)[3], fill = names(prd_vl)[1])) + 
    geom_tile(colour = 'black') + 
    pbase +
    scale_y_discrete(expand = c(0, 0)) + 
    scale_x_discrete(expand = c(0, 0)) +
    scale_fill_distiller(palette = 'Spectral') +
    guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 12, angle = 0)))
  p
}, height = 700, width = 700)
```

>>>>

library(tidyverse)
library(vegan)
library(ggord)
library(scales)
library(effects)
library(shiny)
library(plotly)

@@

prd_vl <- reactive({

  return(prd_vl)

@@

  p <- ggplot(prd_vl(), aes_string(y = names(prd_vl())[2], x = names(prd_vl())[3], fill = names(prd_vl())[1])) + 
    geom_tile(colour = 'black') + 
    theme_bw(base_family = 'serif') +
    pbase +
    scale_y_discrete(expand = c(0, 0)) + 
    scale_x_discrete(expand = c(0, 0)) +
    scale_fill_distiller(palette = 'Spectral') +
    guides(fill = guide_colourbar(barheight = 0.5, barwidth = 15, label.theme = element_text(size = 12, angle = 0)))
  p
}, height = 700, width = 700)

renderPlotly({

  dat <- prd_vl()[, 1] %>% 
    as.matrix

  scene <- list(
    aspectmode = 'manual', 
    aspectratio = list(x = 0.5, y = 1, z = 0.3)
  )

  p <- plot_ly(z = ~dat) %>% add_surface() %>% 
    layout(scene = scene)
  p

})
```
